Dish: Distribution-oblivious Shell Scripting

### 2019-11-22 pldi/draft.tex
Fix

Commands for explicitly specifying parallelism such \ttt{qsub}~\cite{gentzsch2001sun}, \textsc{SLURM}~\cite{yoo2003slurm}, calls to \textsc{GNU} \ttt{parallel}~\cite{Tange2011a}, or any manual rewriting~\cite{mapreduce:08, ciel:11, spark:12}.
These commands require the user to express the program explicitely, work only with embarrasingly parallel (and short) programs;
  \sys and scales out to large pipelines
Often, these commands provide options to support very special cases\footnote{
---a stark contradiction to the celebrated \unix philosophy.
For example, \tti{parallel}, an official GNU project, flags such as \ttt{--skip-first-line}, \ttt{-trim}, and \ttt{--xargs}, that a \unix user would achieve with \ttt{head}, \ttt{sed}, and \ttt{xargs}; it also includes other programs that 
with complex semantics, such as the ability transfer files between computers, separate text files, and parse CSV.

>>>>

Commands for explicitly specifying parallelism such \ttt{qsub}~\cite{gentzsch2001sun}, \textsc{SLURM}~\cite{yoo2003slurm}, calls to \textsc{GNU} \ttt{parallel}~\cite{Tange2011a}, or any manual rewriting~\cite{mapreduce:08, ciel:11, spark:12}.
These commands require the user to express the program explicitely, work only with embarrasingly parallel (and short) programs;
  \sys and scales out to large pipelines
Often, these commands provide options to support very special cases
---a stark contradiction to the celebrated \unix philosophy.
For example, \tti{parallel}, an official GNU project, flags such as \ttt{--skip-first-line}, \ttt{-trim}, and \ttt{--xargs}, that a \unix user would achieve with \ttt{head}, \ttt{sed}, and \ttt{xargs}; it also includes other programs that 
with complex semantics, such as the ability transfer files between computers, separate text files, and parse CSV.
